---
title: "day_10_activities"
author: "Joe DeCesaro"
date: "8/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(ggbeeswarm)
```

Read in the data and convert NAs
```{r}
ice_coverage <- read_csv(here("data", "ntl33_v7.csv"), na = "-999")

wi_met <- read_csv(here("data", "ntl20_v6.csv"))
```

Create a visualization that compares ice duration across different lakes in the Madison Lake Area. Include both the actual ice duration values and some representation of summary statistics for each lake. Careful if you use a boxplot over a jitter or beeswarm - what values might be doubly represented? Can you find an argument that would help you remove those from the boxplot?

```{r}
ggplot(data = ice_coverage, aes(x = lakeid, y = ice_duration)) +
  geom_beeswarm(na.rm = TRUE, aes(color = lakeid)) +
  geom_boxplot(fill = NA,
               color = "navy",
               na.rm = TRUE,
               outlier.colour = NA)
```


